---
title: "Malicious provider simulation with bitcoin exchange data"
author: "Ahmed Ali"
date: "5 November 2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Aim
The aim here is to understand how the MAD (Median absolute deviance) can increase as we have more malicious feed providers attack the system. This will help in narrowing down a set of criteria to develop an algorithm which can stop itself from accepting new values while the the average exchange is deviating significantly from the median.


## Bitcoin - Good providers

Bitcoin data comprises of hourly input data by 26 exchanges from the dates 20/10/2021 to 22/10/2021. The exchanges are:

```{r,echo=FALSE}
library(readxl)
exchange_data <- read_excel("exchange_data.xlsx")
colnames(exchange_data[,c(5:ncol(exchange_data))])
```

We calculate Median Absolute deviance (MAD) of inputs for each time point and plot the density plot to observe the distribution of the MAD.

```{r,echo=FALSE}
exchange_data$median_ex <- apply(exchange_data[,c(5:30)],1,median)
exchange_data$mad_ex <- apply(exchange_data[,c(5:30)],1,mad)


hist(na.omit(exchange_data$mad_ex),freq = FALSE,xlab = "MAD of Input data",main = "")
# Calculate density
dx <- density(na.omit(exchange_data$mad_ex))
# Add density
lines(dx, lwd = 2, col = "red")

```

We observe the data is right skewed with larger values of MAD less likely to occur. Below we can see the summary statistics of the MAD’s and the median MAD is small relative to the prices of bitcoin proposed.

```{r,echo=FALSE}
summary(exchange_data$mad_ex)
```



## Bitcoin - 10% Malicious providers

What does the distribution look like if three of providers are malicious? For the first 3 providers in the data, we will add a simulated value from the uniform distribution between 1000 and 5000 - all values equally likely to happen and added to the current values provided by the exchanges.

```{r,echo=FALSE}
set.seed(123)
exchange_data10 <- exchange_data
for(i in 1:nrow(exchange_data10)){
for(j in 5:7){
  exchange_data10[i,j] = exchange_data10[i,j] + runif(1,-5000,5000) 
  
}
}

exchange_data10$median_ex <- apply(exchange_data10[,c(5:30)],1,median)
exchange_data10$mad_ex <- apply(exchange_data10[,c(5:30)],1,mad)


hist(na.omit(exchange_data10$mad_ex),freq = FALSE,xlab = "MAD of Input data",main = "")
# Calculate density
dx <- density(na.omit(exchange_data10$mad_ex))
# Add density
lines(dx, lwd = 2, col = "red")


```

The distribution is pretty similar in terms of the shape but it seems that average exchanges absolute deviation from the median has shifted to the right. The MADs are still robust at this stage

```{r, echo=FALSE}
summary(exchange_data10$mad_ex)
```


## Bitcoin - 25% Malicious providers

What would the spread of the MAD values look like if we have 25% of the providers as malicious? As before - we simulate values from a uniform distribution and add them to the values of the exchanges. In this scenario we have 7 malicious providers.

```{r,echo=FALSE}
set.seed(123)
exchange_data25 <- exchange_data
for(i in 1:nrow(exchange_data25)){
for(j in 5:11){
  exchange_data25[i,j] = exchange_data25[i,j] + runif(1,-5000,5000) 
  
}
}

exchange_data25$median_ex <- apply(exchange_data25[,c(5:30)],1,median)
exchange_data25$mad_ex <- apply(exchange_data25[,c(5:30)],1,mad)

hist(na.omit(exchange_data25$mad_ex),freq = FALSE,xlab = "MAD of Input data",main = "")
# Calculate density
dx <- density(na.omit(exchange_data25$mad_ex))
# Add density
lines(dx, lwd = 2, col = "red")

```


We now see a bigger impact on the distribution of the MADs with the median further shifted to the right.


```{r,echo=FALSE}
summary(exchange_data25$mad_ex)
```


## Bitcoin - 50% Malicious providers

What would the spread of the MAD values look like if we have 50% of the providers as malicious? As before - we simulate values from a uniform distribution and add them to the values of the exchanges. In this scenario we have 13 malicious providers.

```{r,echo=FALSE}
set.seed(123)
exchange_data50 <- exchange_data
for(i in 1:nrow(exchange_data50)){
for(j in 5:17){
  exchange_data50[i,j] = exchange_data50[i,j] + runif(1,-5000,5000) 
  
}
}

exchange_data50$median_ex <- apply(exchange_data50[,c(5:30)],1,median)
exchange_data50$mad_ex <- apply(exchange_data50[,c(5:30)],1,mad)

hist(na.omit(exchange_data50$mad_ex),freq = FALSE,xlab = "MAD of Input data",main = "")
# Calculate density
dx <- density(na.omit(exchange_data50$mad_ex))
# Add density
lines(dx, lwd = 2, col = "red")

```

At 50% malicious providers - the effect is clear to see. More extremely large MAD values are now part of the distribution and the median has shifted significantly to the right. This is intuitive since half of the data is now considered malicious.

```{r,echo=FALSE}
summary(exchange_data50$mad_ex)
```


## Bitcoin - 90% Malicious providers

We now attempt to modify 23 providers into malicious providers. 

```{r,echo=FALSE}
set.seed(123)
exchange_data90 <- exchange_data
for(i in 1:nrow(exchange_data90)){
for(j in 5:27){
  exchange_data90[i,j] = exchange_data90[i,j] + runif(1,-5000,5000) 
  
}
}

exchange_data90$median_ex <- apply(exchange_data90[,c(5:30)],1,median)
exchange_data90$mad_ex <- apply(exchange_data90[,c(5:30)],1,mad)

hist(na.omit(exchange_data90$mad_ex),freq = FALSE,xlab = "MAD of Input data",main = "")
# Calculate density
dx <- density(na.omit(exchange_data90$mad_ex))
# Add density
lines(dx, lwd = 2, col = "red")

```

Here the effect is even more defined, we see a rough median of 3000 with a large range of possible values.

```{r,echo=FALSE}
summary(exchange_data90$mad_ex)
```



